External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-10 CVPR2017_Review_Unified.tex
add

%%%%%%%%% ABSTRACT
\begin{abstract}
Existing image denoising methods mainly focus on signal independent noise such as Gaussian noise.\ The related paper showed that the internal priors (e.g., self-similarity) are highly effective for removing Gaussian noise from synthetic noisy images.\ However, the noise in real noisy images is much more complex than Gaussian noise since it is signal dependent and from several main sources.\ Hence, the internal priors learned on real noisy images would largely degrade the performance of denoising methods.\ In this paper, we propose to avoid the degradation by employing the external priors to guide the learning of internal priors.\ Specifically, we firstly learn external priors via Gaussian Mixture Model on the patch groups (PGs) extracted from natural clean images, and then employ the external priors to guide the subspace selection and orthogonal dictionary learning of the PGs from given noisy image.\ The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process.\ Extensive experiments on real noisy image denoising demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods. 
\end{abstract}
% in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

Image denoising is an ideal platform for testing computer vision models and an essential procedure for the reliability of many vision systems such as medical imaging and surveillance. It aims to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise. For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning} most of which focusing on additive white Gaussian noise (AWGN). These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.

However, the methods designed for synthetic Gaussian noise is much less effective for removing the noise in real noisy images. The reason is that the noise in real noisy images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.). Besides, by the seminar work of \cite{healey1994radiometric}, the noise in the camera imaging process \cite{NewInCamera,crosschannel2016} are signal dependent and identified by five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. This would largely limit the performance of these methods, which are designed for signal independent noise, on dealing with complex real noise. To prove our argument, we apply some representing methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} on a real noisy image provided in \cite{crosschannel2016}. The testing image is captured by a Nikon D800 camera when ISO is 3200. The ``ground truth" image is also provided with which we can calculate objective measurements such as PSNR. The denoised images of these methods are listed in Figure \ref{fig1} (from (b)$\sim$(f)). One can see that these methods either remove the noise or over-smooth the complex details in real noisy image.

In the last decade, there are also several methods \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} developed for real noisy image denoising. Almost all these methods employ a two-stage framework: firstly estimating the parameters of the assumed noise model (usually Gaussian distribution or mixture of Gaussians (MoG)) and then performing denoising with the help of the estimated noise model. However, the noise in real noisy images are very complex and hard to be modeled by explicit distributions. Therefore, the denoising performance of these methods would be influenced by the error between the estimated noise model and the actual noise distribution. This can be validated by the   denoised results listed in Figure \ref{fig1} ((g) and (h)), in which we evaluate the state-of-the-art real noisy image denoising method Noise Clinic \cite{noiseclinic,ncwebsite} and a commercial denoising software Neat Image \cite{neatimage}. From the results, we can see that the two methods do not perform well on the testing noisy image. These methods only exploit internal priors (e.g., noise prior, self-similarity) for real noisy image denoising and ignore the information of external natural clean images. 
\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3.5mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

The external priors in natural clean images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internalwould naturally achieves better performance. Based on above considerations, in this paper, we propose to employ the external priors learned from natural clean images to guide the learning of internal priors of given noisy image.\ The flowchart of the proposed method is illustrated in Fig.\ \ref{fig2}.\ In the external stage, we learn the external priors of patch groups \cite{pgpd} since nonlocal self-similarity is successfully used in many denoising methods \cite{nlm,bm3d,wnnm,pgpd}.\ The learning of external priors is performed by Gaussian Mixture Model. In the internal stage, the learning of internal priors includes Gaussian selection and orthogonal dictionary learning (DL).\ The internal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. The image denoising is simultaneously done with the DL process.\ Both of the two stages have closed-form solutions.\ Hence, our proposed denoising method is very efficient.\ Through extensive experiments on real noisy image denoising, we demonstrate that the proposed method achieves better performance on real image denoising.

The rest of this paper will be summarized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we perform extensive experiments on real image denoising problem; in Section 4, we conclude our paper and give future work.

@@

In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem. In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called ``Noise Clinic" \cite{noiseclinic,ncwebsite}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.

@@

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{41.39}  & 667.36 & 44.06
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Most of existing image denoising methods use some statistical models such as additive white Gaussian noise (AWGN) to model the noise, and learn image priors from either external data or the noisy image itself to remove noise. However, the noise in real-world noisy images is much more complex than AWGN, and it is hard to be modeled by simple analytical distributions. Therefore, many state-of-the-art denoising methods in literature become much less effective when applied to real noisy images. In this paper, we develop a robust denoiser for real noisy image denoising without explicit assumption on noise models. Specifically, we first learn external priors from a set of clean natural images, and then use the learned external priors to guide the learning of internal latent priors from the given noisy image. The proposed method is simple yet highly effective. Experiments on real noisy images demonstrate that it achieves much better denoising performance than state-of-the-art denoising methods, including those designed for real noisy images.
\end{abstract}

@@

Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems. In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging. In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise. Numerous image denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.

Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise n to be additive white Gaussian noise (AWGN). Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.). According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}. One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.

There have been a few methods \cite{Liu2008,almapg,Zhu_2016_CVPR,crosschannel2016,noiseclinic,ncwebsite,neatimage} developed for real noisy image denoising. Almost all of these methods follow a two-stage framework: first estimate the parameters of the assumed noise model (usually Gaussian  or mixture of Gaussians (MoG)), and then perform denoising with the estimated noise model. Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoised results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}. One can see that these two methods do not perform well on this noisy image either.

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3.5mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

\begin{figure}\vspace{-0.1in}
\centering
\includegraphics[width=0.9\linewidth]{Flowchart.png}
\vspace{-0.1in}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-0.2in}
\label{fig2}
\end{figure}

This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models. To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image. The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}. We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior. The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then a hybrid orthogonal dictionary (HOD) is learned as the internal prior for image denoising. Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.

@@

In the last decade, researchers proposed many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. The method of ``Noise Clinic" \cite{noiseclinic,ncwebsite} and the software of Neat Image \cite{neatimage} are developed specifically for real noisy image denoising. ``Noise Clinic" \cite{noiseclinic,ncwebsite} generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.

@@

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{39.57}  & 667.36 & 43.77
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}
